The Castro AMR Simulation Code: Current and Future Developments

### 2019-10-10 astronum_2019_Castro/astronum-castro-2019.tex
Reword Summit vs Cori Haswell comparison to make it clear which direction we are quoting a speedup.

The large increase in performance of the code when run on GPUs enables
us to do away with the flame boosting.  All of the physics solvers
needed for the XRB simulations run on the GPUs: the hydrodynamics,
explicit diffusion, realistic equation of state and conductivities,
and the 13-isotope He burning network we are using.  Preliminary
estimates show that we can expect a speed-up of at least $5\times$ when
comparing the NERSC Cori Haswell nodes (using CPUs) to the OLCF Summit
nodes (using GPUs).  Work is underway to further optimize the GPU code,
especially the reaction networks.

>>>>

The large increase in performance of the code when run on GPUs enables
us to do away with the flame boosting.  All of the physics solvers
needed for the XRB simulations run on the GPUs: the hydrodynamics,
explicit diffusion, realistic equation of state and conductivities,
and the 13-isotope He burning network we are using.  Preliminary
estimates show that we can expect a speed-up of at least $5\times$ for the OLCF Summit
nodes (using GPUs) over the NERSC Cori Haswell nodes (using CPUs).
Work is underway to further optimize the GPU code,
especially the reaction networks.
